Context Inconsistency Management \\in Pervasive Systems

### 2011-04-12 paper/paper.tex
tweak

In this paper we present two complementary approaches for improving the mitigation of context inconsistencies. 
First we present partial constraint checking for timely identifying context inconsistencies at runtime. An extra constraint layer is added to the traditional ontology based context model and conflicts can be detected by locally checking partial constraints in the ontology. This dramatically improves performance compared to iterative evaluation of an entire ontology~\cite{xu:2010:PCC}.
Secondly we discuss the extension of the traditional ontology model with context life cycles to more accurately represent the environment of context-aware applications. This information can then be used to estimate the relative reliability of contexts in a conflict set and discard the contexts with lowest reliability~\cite{bu:2006:CCM}. 
Apart from resolving context conflicts it is also possible to represent inconsistencies into the context model itself~\cite{ko:2009:IOFO}. In this paper we present a use case in which we explore the possibilities of incorporating inconsistencies into context models using fuzzy ontologies.
} % end of abstract

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%% START OF THE PAPER %%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

In this paper we present two complementary approaches for improving the mitigation of context inconsistencies. 
First we present partial constraint checking for timely identifying context inconsistencies at runtime. An extra constraint layer is added to the traditional ontology based context model and conflicts can be detected by locally checking partial constraints in the ontology. This dramatically improves performance compared to iterative evaluation of an entire ontology~\cite{xu:2010:PCC}.
Secondly we discuss the extension of the traditional ontology model with context life cycles to more accurately represent the environment of context-aware applications. This information can then be used to estimate the relative reliability of contexts in a conflict set and discard the contexts with lowest reliability~\cite{bu:2006:CCM}. 
Apart from resolving context conflicts it is also possible to represent inconsistencies into the context model itself~\cite{ko:2009:IOFO}. In this paper we present a case study in which we explore the possibilities of incorporating inconsistencies into context models using fuzzy ontologies.
} % end of abstract

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%% START OF THE PAPER %%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
